Поддержка жестов мышью в мета-CASE-системах

### 2010-10-15 articles/mouseGestures/article.tex
Библиография по требованиям сборника кафедры.

\begin{thebibliography}{9001}
  \bibitem{levenshtein} В.И. Левенштейн. Двоичные коды с исправлением выпадений, вставок и замещений символов // Доклады Академий Наук СССР, 1965. 163.4:845-848
  \bibitem{qreal} А.Н. Терехов, Т.А. Брыксин, Ю.В. Литвинов и др., Архитектура среды визуального моделирования QReal. // Системное 
программирование. Вып. 4: Сб. статей / Под ред. А.Н.Терехова, Д.Ю.Булычева. --- СПб.: 2009, с. 171-196
  \bibitem{svm1} Aizerman, M., Braverman, E., Rozonoer, L., Theoretical foundations of the potential function method in pattern recognition learning, 
Automation and Remote Control 25, 1964, pp. 821–837
  \bibitem{neuronet1} Bishop, C.M., Neural Networks for Pattern Recognition, Oxford: Oxford University Press, 1995  
  \bibitem{chaosAlgorithm} Brun, D., Mouse gesture recognition // ByteArray.org Actionscript 3 Experiments. URL: http://www.bytearray.org/?p=91 
  \bibitem{svm2} Catanzaro, B., Sundaram N., Keutzer K., Fast Support Vector Machine Training and Classification on Graphics Processors, International 
Conference on Machine Learning, 2008
  \bibitem{neuronet3} Faaborg, A.J., Using Neural Networks to Create an Adaptive Character Recognition System, Cornell University, Ithaca, NY, 2002
  \bibitem{boosting1} Freund, Y., Schapire, R.E., A Short Introduction to Boosting, AT\&T Labs Research, 1999
  \bibitem{boosting2} Li, S.Z., Zhang, Z., FloatBoost Learning and Statistical Face Detection, IEEE Transactions on Pattern Analysis and Machine Intelligence, 2004
  \bibitem{nns1} Potamias, M., Athitsos, V. , Nearest Neighbor Search Methods for Handshape Recognition, PETRA, 2008
  \bibitem{hmm1} Rabiner, Lawrence R., A tutorial on hidden Markov models and selected applications in speech recognition, Proceedings of the IEEE, 1989, pp. 257-286
  \bibitem{neuronet2} Ripley, B.D., Pattern Recognition and Neural Networks, Cambridge University Press, 1996
  \bibitem{hmm2} Starner, T., Pentland, A., Visual Recognition of American Sign Language Using Hidden Markov Models, MIT, 1995
  \bibitem{nns2} Shakhnarovish, Darrell, and Indyk, Nearest-Neighbor Methods in Learning and Vision, MIT Press, 2005
  \bibitem{qtGestures} Thelin, J., Recognizing mouse gestures, Qt online reference documentation, URL: http://doc.trolltech.com/qq/qq18-mousegestures.html 
  \bibitem{hmm3} Vlontzos, J.A., Kung, S.Y., Hidden Markov models for character recognition, IEEE Transactions on Image Processing, 1992
\end{thebibliography}

>>>>

\begin{thebibliography}{9001}
  \bibitem{levenshtein} В.И. Левенштейн. Двоичные коды с исправлением выпадений, вставок и замещений символов // Доклады Академий Наук СССР, 1965. 163.4:845-848
  \bibitem{qreal} А.Н. Терехов, Т.А. Брыксин, Ю.В. Литвинов и др., Архитектура среды визуального моделирования QReal. // Системное программирование. Вып. 4. СПб.: Изд-во СПбГУ. 2009, С. 171-196
  \bibitem{svm1} Aizerman, M., Braverman, E., Rozonoer, L., Theoretical Foundations of the Potential Function Method in Pattern Recognition Learning // Automation and Remote Control 25, 1964, P. 821–837.
  \bibitem{neuronet1} Bishop, C., Neural Networks for Pattern Recognition // Oxford: Oxford University Press, 1995, 482 pp.
  \bibitem{chaosAlgorithm} Brun, D., Mouse Gesture Recognition // ByteArray.org Actionscript 3 Experiments. URL: http://www.bytearray.org/?p=91 
  \bibitem{svm2} Catanzaro, B., Sundaram N., Keutzer K., Fast Support Vector Machine Training and Classification on Graphics Processors // Proceedings of the 25th International Conference on Machine Learning (ICML 2008) (2008), P. 104-111.
	\bibitem{neuronet3} Faaborg, A., Using Neural Networks to Create an Adaptive Character Recognition System // Cornell University, Ithaca, NY, 2002
  \bibitem{boosting1} Freund, Y., Schapire, R., A Short Introduction to Boosting // Japanese Society for Artificial Intelligence, Vol. 14, No. 5. (1999), P. 771-780.
  \bibitem{boosting2} Li, S., Zhang, Z., FloatBoost Learning and Statistical Face Detection // IEEE Transactions on Pattern Analysis and Machine Intelligence, Vol. 26, No. 9. 2004. P. 1112-1123.
  \bibitem{nns1} Potamias, M., Athitsos, V., Nearest Neighbor Search Methods for Handshape Recognition // Proceedings of the 1st international conference on PErvasive Technologies Related to Assistive Environments (PETRA), Vol. 282. 2008
  \bibitem{hmm1} Rabiner, Lawrence R., A Tutorial on Hidden Markov Models and Selected Applications in Speech Recognition // Proceedings of the IEEE, 1989, P. 257-286.
  \bibitem{neuronet2} Ripley, B., Pattern Recognition and Neural Networks // Cambridge University Press. 1996. 416 pp.
  \bibitem{hmm2} Starner, T., Pentland, A., Visual Recognition of American Sign Language Using Hidden Markov Models // International Workshop on Automatic Face and Gesture Recognition. 1995. P. 189-194.
  \bibitem{nns2} Shakhnarovish, Darrell, and Indyk, Nearest-Neighbor Methods in Learning and Vision // MIT Press. 2005. 262 pp.
  \bibitem{qtGestures} Thelin, J., Recognizing Mouse Gestures // Qt Online Reference Documentation, URL: http://doc.trolltech.com/qq/qq18-mousegestures.html 
  \bibitem{hmm3} Vlontzos J., Kung, S., Hidden Markov Models for Character Recognition // IEEE Transactions on Image Processing, Vol. 1, No. 4. 1992. pp. 539-543.
\end{thebibliography}
